My title

### 2022-02-28 outputs/paper/paper.Rmd
Update LGBT analysis

The percentage of LGBT (and many other genders) has risen in recent years in the US, probably related to propaganda and political correctness.

@@

LGBT is the acronym of the following 4 genders, **L** for Lesbian, **G** for gay, **B** for bisexual, **T** for transgender. By definition, these genders by definition should have a much lower birth rate than heterosexual. Then change in birth rate and change in LGBT population should have a negative propotional relationship (i.e. Growth in LGBT population leads to lower birth rate).
Thus, the population changes in these population are very likely to make an impact on the birth rate of the US.

@@

Figure \@ref(fig:fig-gender-raising-children-distribution) shows the gender distribution of LGBT and Same Sex Couple as well as the percentage raising children.
Figure \@ref(fig:fig-gender-raising-children-distribution) (a) and Figure \@ref(fig:fig-gender-raising-children-distribution) (c) clearly shows that more females are non-heterosexual.
This should make a even larger impact ($\phi<-1$) on birth rate as only females are able to give births (in normal situations).

Figure \@ref(fig:fig-gender-raising-children-distribution) (b) shows the percentage of LGBT population that raise children. 71% of the LGBT population don't raise children.

>>>>

The percentage of LGBT (and many other gender identities) population has risen in recent years in the US, probably related to propaganda and political correctness.

@@

LGBT is the acronym of the following 4 gender identities, **L** for Lesbian, **G** for gay, **B** for bisexual, **T** for transgender. By definition, these genders should have a much lower birth rate than heterosexual. Then change in birth rate and change in LGBT population should have a negative propotional relationship (i.e. Growth in LGBT population leads to lower birth rate).
Thus, the population changes in these population are very likely to make an impact on the birth rate of the US.

@@

Figure \@ref(fig:fig-gender-raising-children-distribution) shows the gender distribution of LGBT and Same Sex Couple as well as the percentage raising children.
Figure \@ref(fig:fig-gender-raising-children-distribution) (a) and Figure \@ref(fig:fig-gender-raising-children-distribution) (c) clearly shows that more females are non-heterosexual.
This should make a even larger impact ($\phi<-1$) on birth rate as only females are able to give births (in normal situations).
went
Figure \@ref(fig:fig-gender-raising-children-distribution) (b) shows the percentage of LGBT population that raise children. 71% of the LGBT population don't raise children.
